Tensor denoising and completion based on ordinal observations

### 2020-06-06 paper/ICML/supplements/latexsource/ordinalTv4.tex
update

\section{Introduction}
Multidimensional arrays, a.k.a.\ tensors, arise in a variety of applications including recommendation systems~\citep{baltrunas2011incarmusic}, social networks~\citep{nickel2011three}, genomics~\citep{wang2019three}, and neuroimaging~\citep{zhou2013tensor}. There is a growing need to develop general methods for analyzing these noisy, high-dimensional datasets that can handle two main problems. The problem of tensor denoising -- which aims to recover a signal tensor from its noisy entries -- has gained increased attention in theory and applications~\citep{hong2018generalized,wang2019multiway}. The second problem, tensor completion, examines the minimum number of entries needed for a consistent recovery~\citep{ghadermarzy2018learning,montanari2018spectral}. Low-rankness is imposed to the signal tensor, thereby efficiently reducing the intrinsic dimension in both problems.

>>>>

\section{Introduction}
Multidimensional arrays, a.k.a.\ tensors, arise in wide applications including recommendation systems~\citep{baltrunas2011incarmusic}, social networks~\citep{nickel2011three}, genomics~\citep{wang2019three}, and neuroimaging~\citep{zhou2013tensor}. There is a growing need to develop general methods that can address two main problems for analyzing these noisy, high-dimensional datasets. The problem of tensor denoising -- which aims to recover a signal tensor from its noisy entries -- has gained increased attention in theory and applications~\citep{hong2018generalized,wang2019multiway}. The second problem, tensor completion, examines the minimum number of entries needed for a consistent recovery~\citep{ghadermarzy2018learning,montanari2018spectral}. Low-rankness is often imposed to the signal tensor, thereby efficiently reducing the intrinsic dimension in both problems.
